Introducing Statistical Design of Experiments to SPARQL Endpoint Evaluation

### 2013-05-04 exp1/iswc2013.tex
more on setup
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@499 43ef1190-90fd-4dd7-a769-d0121f02b80e

\section{Experimental setup}

@@

>>>>

\section{Experimens}

\subsection{Setup}

@@

The experimentation is implemented in R\todo{ref}, which is a free
software environment for statistical computing and graphics. Necessary
tools for DoE has been implemented by the R community in packages
called DoE.base, BsMD and FrF2. The experiments are run on a third
computer in a 1 gigabit LAN with the two experiment hosts.  As
response variable, we have chosen to use the time from the namespace
server lookup to the data has been transferred. This choice is
somewhat arbitrary, many other response variables could be chosen, and
indeed, future work should explore multi-variable responses, but for
simplicity, we think this reflects the total amount of work done by
the SPARQL endpoint well. For the measurements, we have chosen to use
the RCurl package, which is a thin wrapper around the curl
library. Curl has  good facilities for timing requests, and so
we rely on its measurements.

\subsection{Full factorial experiment}

\subsection{Fractional factorial experiment}

\subsection{Fractional factorial experiment with more data}
